User-level Grid Monitoring with Inca 2

### 2007-02-23 pubs/papers/hpdc-gmw-2007/paper.tex
merge tg section into paper.tex
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6547 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

@@

>>>>

TeraGrid's Coordinated TeraGrid Software and Services (CTSS) was designed to
allow users to more easily run Grid jobs across its distributed, heterogeneous
resources.  CTSS is available from all TeraGrid compute resources and is
comprised of approximately 30 software packages for Grid services (gridftp, ws
gram), Grid jobs (gridshell, myproxy, globus), cluster tools (pacman, tgusage),
data management (srb, hdf5) and user applications (mpich, gcc).

In order to validate and verify CTSS functionality from a user perspective,
TeraGrid and SDSC developed and deployed Inca 1 on TeraGrid in 2003. TeraGrid
transitioned to Inca 2 in 2006 and, in addition to CTSS monitoring, began using
Inca to collect job usage information from Globus 2 GRAM logs and to detect
expired host and CA certificates and CA CRLs to its Inca deployment.

@@

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.
